%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.
    % The font could be set to Windows-specific Calibri by using the 'calibri' option
    \documentclass[]{mcdowellcv}

    % For mathematical symbols
    \usepackage{amsmath}
    
      % Set applicant's personal data for header
      \name{Zachary Morello \linebreak \normalfont\small{zacharymorello.com}}
      \address{zm.morello@gmail.com \linebreak 5037042422}
      \contacts{Github: zachary-morello \linebreak LinkedIn: morelloz}
    
    \begin{document}
% Print the header
\makeheader
\vspace{-4pt}

\begin{cvsection}{Education}
	\begin{cvsubsection}{Oregon State University}{}{Sep 2017 - Jun 2021}
        \vspace{-4pt}
		\begin{itemize}
			\item BS in Computer Science. GPA: 3.5
                \item OSU Game Development Club President (2020-2021)
		\end{itemize}
        \vspace{-12pt}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Employment}
      \begin{cvsubsection}{Full Stack Software Engineer}{HP Inc.}{Aug 2024 -- Present}
    \vspace{-4pt}
		\begin{itemize}%
            \item Worked with a team of 20+ engineers to develop a collaborative container building and deployment app "AI Studio" using Golang as the backend and React as the frontend.
            \begin{itemize}
                \item Enabled both technical and nontechnical users to build and deploy OCI-compliant container images for data science workloads, following industry best practices.
                \item Designed and implemented CI/CD pipelines with GitHub Actions, achieving rapid automated testing and deployment, and resolving critical production bugs within the same day.
                \item Led refactoring of legacy code while introducing new features, improving code quality and maintainability through best practice guidance.
                \item Developed a dedicated Python service to run MongoDB analytics pipelines, providing actionable user behavior insights.
                \item Maintained 80\% code coverage with robust, maintainable unit tests, supporting high reliability and rapid development.
            \end{itemize}
		  \end{itemize}
	   \end{cvsubsection}
    \vspace{-6pt}
     \begin{cvsubsection}{Systems Engineer}{HP Inc.}{Jun 2021 -- Aug 2024}
            \vspace{-4pt}
          \begin{itemize}%
              \item Developed major features of a forecasting web application using C\# in ASP.NET that served over 100 managers within the company.
                \begin{itemize}%
                    \item Achieved a 500\% speed improvement in data exports by refactoring SQL queries and implementing multi-threading. Created an inheritable class for future export development.
                    \item Implemented fail-safes that prevent service crashes on low performance hardware, ensuring they wait for sufficient memory before execution.      
                \end{itemize} 
            \end{itemize}
            \begin{itemize}%
            \item Headed development of a change management Blazor app and created an interactive Figma prototype to facilitate user feedback sessions.
                \begin{itemize}%
                    \item Worked with subject matter experts on reverse engineering the original application. From that work, created a requirements document that has been leveraged on other projects.
                    \item Adapted prototype into a user interface with Blazor Webassembly and C\#.
                \end{itemize} 
            \item Led discussions about software engineering standards, leveraging new technologies for our projects and wrote documentation to ensure sustainable code practices within the team.
            \end{itemize}    
    \end{cvsubsection}
        \end{cvsection}
        \vspace{-4pt}
\begin{cvsection}{Personal Projects}
  	\end{cvsubsection}
         \vspace{-4pt}
  	\begin{cvsubsection}{Psycho Sphere (Unity Game)}{}{Jun 2023 - Present}
        \vspace{-5pt}

        \begin{itemize}
          \item Created a fully 3D turn based RPG in C# using Unity, with a unique battle system that combines actor placement, physics, and environmental interactions.
          \item Developed a robust set of development tools to streamline level design and game balancing.
          \item Designed a modular AI system that allows for plug-and-play behavior trees that turn simple state machines into complex, emergent behaviors.
        \end{itemize}
	\end{cvsubsection}
         \vspace{-4pt}
  	\begin{cvsubsection}{JermaKart}{}{Sep 2020 - Jun 2021}
        \vspace{-5pt}

        \begin{itemize}
          \item Published and supported a fully featured MarioKart style game developed in C# using Unity, with a self-constrained development period of one month.
          \item Designed a tactile UI with QoL features such as a volume mixer and a carousel level select screen.
          \item Used reinforcement learning to create AI opponents with the ability to navigate complex racetracks.
        \end{itemize}
	\end{cvsubsection}
 \vspace{-6pt}
\end{cvsection}
\begin{cvsection}{Technical Skills}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item Languages: Golang, C\#, C++, Python, Typescript, MongoDB, SQL
			\item Frameworks and Libraries: Wails, Containerd, ASP.NET, Blazor, Tensorflow, Pytorch, Node.js
			\item Tools: Agile, Figma, Git, Azure Devops CI/CD, Copilot, Linux, Visual Studio, Unity, Unreal
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\end{document}